Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2021-01-20 manuscript/ERL_global_C_review.Rmd
worked on schematic and its coordination with results figures
#61 , #64

Forest C cycling varies enormously across biomes, which are artificial categorical distinctions convenient for categorizing the world's forests according to major differences in climate, vegetation, *etc.* 
Since the early 19th century, it has been recognized that climate plays a dominant role in shaping differences among forests on a global scale [@humboldt_essay_1807; @holdridge_determination_1947].
Early quantitative syntheses revealed that C fluxes such as net primary productivity ($NPP$) decrease dramatically with latitude, or increase across gradients of mean annual temperature and, to a lesser extent, precipitation [@lieth_primary_1973].

@@

In the past *couple of/several* decades, researchers have started asking how age trends--mostly in biomass accumulation-- vary across biomes.
*(look up early work on this--citations in @anderson_temperature-dependence_2006)*
@anderson_temperature-dependence_2006
@chazdon_carbon_2016
@cook-patton_mapping_2020
There has been little synthesis of differences in variables other than C stocks or their accumulation rates.
Given the important role of secondary forests in the current and future global C cycle, concrete understanding of age trends in C fluxes and stocks and how these vary across biomes is critical to better understandign of the global C cycle.

```{r schematic, eval = generate_figures, echo=FALSE, fig.align = "center", fig.cap = "Figure 1 | DRAFT Schematic diagram summarizing current understanding of biome differences and age trends in forest C cycling. Plotted values are realistic with respect to the results of this synthesis, but schematic is not intended to be quantitatively precise. ", out.width='100%', fig.pos='H'}

>>>>

Forest C cycling varies enormously across biomes, which are artificial categorical distinctions convenient for categorizing the world's forests according to major differences in climate, vegetation, *etc.* 
Since the early 19th century, it has been recognized that climate plays a dominant role in shaping differences among forests on a global scale [@humboldt_essay_1807; @holdridge_determination_1947].
*C stocks*
Early quantitative syntheses revealed that C fluxes such as net primary productivity ($NPP$) decrease dramatically with latitude, or increase across gradients of mean annual temperature and, to a lesser extent, precipitation [@lieth_primary_1973].

@@

In the past *couple of/several* decades, researchers have started asking how age trends--mostly in biomass accumulation-- vary across biomes.
*(look up early work on this--citations in @anderson_temperature-dependence_2006)*
@anderson_temperature-dependence_2006
@chazdon_carbon_2016
@cook-patton_mapping_2020
There has been little synthesis of differences in variables other than C stocks or their accumulation rates.
Given the important role of secondary forests in the current and future global C cycle, concrete understanding of age trends in C fluxes and stocks and how these vary across biomes is critical to better understanding of the global C cycle.

```{r schematic, eval = generate_figures, echo=FALSE, fig.align = "center", fig.cap = "Figure 1 | Schematic diagram summarizing current understanding of biome differences and age trends in forest C cycling. Variables are defined in Table 1. Age trends, which represent idealized dynamics following a disturbance that removes all living and non-living vegetation, are an updated version of the classic figure from Odum (1969), with heavy lines corresponding to those in Odum's figure and $NEP$ corresponding to Odum's 'net production'. Here, $NEP$ conists primarily of woody aboveground net primary production ($ANPP_{woody}$), while $ANPP_{woody.turnover}$ is the sum of woody mortality and branch turnover ", out.width='100%', fig.pos='H'}
